---
title: "Section5"
author: "AO XU"
date: "2022-11-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#install.packages('keras')
library(keras)
#install_keras()
```
```{r}
library(tensorflow)
tf$constant('Hello world')
```

```{r}
# packages
library(tidyverse)
library(tidymodels)
library(tidytext)
library(keras)
library(tensorflow)

# data location
url <- 'https://raw.githubusercontent.com/pstat197/pstat197a/main/materials/labs/lab6-nn/data/claims-clean.csv'

# read in data
clean <- read_csv(url)
```
```{r}
# partition
set.seed(102722)
partitions <- clean %>%
  mutate(text_clean = str_trim(text_clean)) %>%
  filter(str_length(text_clean) > 5) %>%
  initial_split(prop = 0.8)
```
```{r}
train_dtm <- training(partitions) %>%
  unnest_tokens(output = 'token', 
                input = text_clean) %>%
  group_by(.id, bclass) %>%
  count(token) %>%
  bind_tf_idf(term = token, 
              document = .id, 
              n = n) %>%
  pivot_wider(id_cols = c(.id, bclass), 
              names_from = token, 
              values_from = tf_idf,
              values_fill = 0) %>%
  ungroup()
```

Logistic regression as NN
```{r}
# extract first ten features
x_train <- train_dtm %>%
  ungroup() %>%
  select(-.id, -bclass) %>%
  select(1:10) %>%
  as.matrix()

# extract labels and coerce to binary
y_train <- train_dtm %>% 
  pull(bclass) %>%
  factor() %>%
  as.numeric() - 1
```

Model specification

Model architecture is defined layer-by-layer. Keras has some preconfigured model types: for feedforward networks, use keras_model_sequential() .

```{r}
# specify model type
model <- keras_model_sequential(input_shape = 10)
```
```{r}
summary(model)
```

```{r}
# add output layer
model <- model %>% layer_dense(1) 
```
```{r}
summary(model)
```
```{r}
model <- model %>% 
  layer_activation(activation = 'sigmoid')
```
Model configuration

Configuring a keras model consists in equipping it with a loss and an optimization method. Optionally, metrics that you’d like computed at each training epoch can be included.

```{r}
model %>% compile(
  loss = 'binary_crossentropy',
  optimizer = optimizer_sgd(),
  metrics = 'binary_accuracy'
)
```
```{r}
history <- model %>%
  fit(x = x_train, 
      y = y_train,
      epochs = 10)
```

```{r}
# retrieve weights
# get_weights(model)
```

```{r}
# evaluate on specified data
evaluate(model, x_train, y_train)
```

```{r}
# compute predictions
model(x_train) %>% head()
```
Single-layer network
```{r}
# store full DTM as a matrix
x_train <- train_dtm %>%
  select(-bclass, -.id) %>%
  as.matrix()
```

```{r}
model <- keras_model_sequential(input_shape = ncol(x_train)) %>%
  layer_dense(10) %>%
  layer_dense(1) %>%
  layer_activation(activation = 'sigmoid')

summary(model)
```
```{r}
model %>%
  compile(
    loss = 'binary_crossentropy',
    optimizer = optimizer_sgd(),
    metrics = 'binary_accuracy'
  )
```

```{r}
history <- model %>%
  fit(x = x_train,
      y = y_train,
      epochs = 50)

plot(history)
```
```{r}
# change the optimizer
model %>%
  compile(
    loss = 'binary_crossentropy',
    optimizer = 'adam',
    metrics = 'binary_accuracy'
  )

# re-train
history <- model %>%
  fit(x = x_train,
      y = y_train,
      epochs = 10)

plot(history)
```
Validation data
```{r}
# redefine model
model <- keras_model_sequential(input_shape = ncol(x_train)) %>%
  layer_dense(10) %>%
  layer_dense(1) %>%
  layer_activation(activation = 'sigmoid')

model %>%
  compile(
    loss = 'binary_crossentropy',
    optimizer = 'adam',
    metrics = 'binary_accuracy'
  )

# train with validation split
history <- model %>%
  fit(x = x_train,
      y = y_train,
      epochs = 20,
      validation_split = 0.2)

plot(history)
```


